---
name: Ty J.
surname: Werdel
position: "Vice Chancelor's Postdoctoral Fellow"
address: "Department of Rangeland, Wildlife and Fisheries Management - Texas A&M University, College Station, TX"
profilepic: "headshot2.jpg"
www: "werdelwildlife.com"
department: "rwfm.tamu.edu/people/werdel-ty/"
email: "ty.werdel@ag.tamu.edu"
github: tywerdel
linkedin: tywerdel
orcid: 0000-0003-4023-9668
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 500000
aboutme: "My research interests include the fields of Wildlife Management and Landscape Ecology. This work addresses questions that provide insight into the relationships between wildlife, native environments, and contemporary human-modified landscapes. I am also interested in software programming to advance my professional acumen, with this CV being compiled with code."
docname: CV
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
require(xfun)
packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data structure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative File Paths
             ,'readr'     # Data Loading
             ,'glue'      # String Manipulation
            )
xfun::pkg_attach2(packages, message = FALSE)
source(file = here("","data.R"))
```

# Education

```{r EDUCATION}
edu %>%
  detailed_entries(
    with = inst,
    what = degree,
    why = detail,
    when = glue::glue("{endYear}",.na = ""),
    where = where
  )
```
# Certifications

```{r CERTIFICATIONS}
certifications %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```

# Employment

```{r EMPLOYMENT}
work %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )
```

# Teaching Experience

```{r WORKS}
teach %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```

# Publications

## *Peer-Reviewed*

Hessami, M.A., **T.J. Werdel**, S.J. Hoagland, and M.T. Kohl. ***In Press***. Melding Past, Present, and Future: The importance of tribal management in wildlife conservation and management. Chapter 1 in E. Gomez and C. Bishop, eds. Wildlife Management and Conservation in North America: An Overview. 

**Werdel, T.J.**, C.W. Piper, A.M. Ricketts, M.S. Peek, and A.A. Ahlers. ***2022***. Scale-specific landscape effects impose range-limiting constraints on the distribution of swift fox.  Landscape Ecology, 37(8), 2065–2079. https://doi.org/10.1007/s10980-022-01466-0

**Werdel, T.J.**, J.A. Jenks, J.T. Kanta, C.P. Lehman, and T.J. Frink. ***2021***. Space use and movement patterns of translocated bighorn sheep. Mammalian Biology, 101(3),329–344. https://doi.org/10.1007/s42991-021-00107-4

**Werdel, T.J.**, J.A. Jenks, T.E. Besser, J.T. Kanta, C.P. Lehman, and T.J. Frink. ***2019***. Restoration of a bighorn sheep population impeded by Mycoplasma ovipneumoniae exposure. Restoration Ecology, 28(2), 387–395. https://doi.org/10.1111/rec.13084 (Cover Article)

**Werdel, T.J.**, J.A. Jenks, T.E. Besser, J.T. Kanta, C.P. Lehman, and T.J. Frink. ***2018***. Survival of translocated bighorn sheep in the Deadwood region of the Black Hills, South Dakota. Northwestern Naturalist,99(3),222–231. https://doi.org/10.1898/NWN18-06.1
\vspace{1\baselineskip}

## *In-Revision*

Palomo-Muñoz, G., **T.J. Werdel**, C.W. Piper, M.S. Peek, A.M. Ricketts, and A.A Ahlers. Spatiotemporal distributions of mammals occurring in an agro-prairie ecosystem. Ecology.

**Werdel, T.J.**, C.W. Piper, A.M. Ricketts, M.S. Peek, and A.A Ahlers. Landscape-scale effects structure carnivore communities in an agro-prairie ecosystem. Journal of Mammalogy.

Piper, C.W., **T.J. Werdel**, M.S. Peek, A.M. Ricketts, D.S. Sullins, and A.A. Ahlers. Landscape composition and proximity to water structure American badger distributions in shortgrass prairies. Journal of Mammalogy.

\vspace{1\baselineskip}
## *In-Review*

**Werdel, T.J.**, J.A. Jenks, J.T. Kanta, C.P. Lehman, and T.J. Frink. Resource 			selection and herbaceous biomass at foraging sites of translocated bighorn sheep.			Rangeland Ecology and Management.

**Werdel, T.J.**, M. Fidino, C.W. Piper, A.M. Ricketts, M.S. Peek, and A.A Ahlers. Landscape composition mediates spatiotemporal interactions among sympatric canids in a prairie ecosystem. Ecological Applications.

**Werdel, T.J.**, C.W. Piper, A.M. Ricketts, M.S. Peek, D.S. Sullins, and A.A Ahlers. Strategic grassland conservation to improve conservation outcomes for swift foxes in a multi-use landscape. Biological Conservation.

# Honors & Awards

## *Total Scholarship ($121,150)*
```{r HONORS}
honors %>%
  detailed_entries(
    with = inst,
    what = degree,
    why = detail,
    when = glue::glue("{endYear}",.na = ""),
    where = where
  )
```

# Professional Service

## *External Journal Reviewer*

```{r REVIEW}
reviewer %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )
```

## *Executive Service in Professional Organizations*

```{r SERVICE}
service %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )
```

## *Working Group Membership*

```{r GROUP}
group %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )
```

## *Chapter Membership*

```{r CHAPTER}
chapter %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )
```

## *Professional Organization Membership*

```{r ORGANIZATION}
organization %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )
```


# Presentations

## *Contributed*

**Werdel, T.J.**, C.W. Piper, A.M. Ricketts, M. Peek, and A.A. Ahlers. **2021**. Scale-specific landscape effects impose range-limiting constraints on the distribution of swift foxes. The Wildlife Society 28th Annual Conference. Virtual.

Piper, C.W, **T.J. Werdel**, A.M. Ricketts, D. Sullins, M. Peek, and A.A. Ahlers. **2021**. Landscape composition and proximity to water structure American badger distributions in shortgrass prairies. The Wildlife Society 28th Annual Conference. Virtual.

**Werdel, T.J.**, C.W. Piper, A.M. Ricketts, M. Peek, and A.A. Ahlers. **2021**. Multiscale landscape effects impose range-limiting constraints on the distribution of swift fox. Swift Fox Conservation Team Meeting, Kansas, USA.

**Werdel, T.J.**, C.W. Piper, A.M. Ricketts, M. Peek, and A.A. Ahlers. **2021**. Multiscale landscape effects impose range-limiting constraints on the distribution of swift fox. Midwest Association of Fish and Wildlife Agencies Furbearer Workshop. Michigan, USA.

Piper, C.W., **T.J. Werdel**, A.M. Ricketts, M. Peek, and A.A. Ahlers. **2021**. Landscape composition and proximity to water structure American badger (Taxidea taxus) distributions in shortgrass prairies. Midwest Association of Fish and Wildlife Agencies Furbearer Workshop. Michigan, USA.

**Werdel, T.J.**, A.M. Ricketts, M. Peek, and A.A. Ahlers. **2020**. Assessing factors that influence occupancy and colonization of swift fox in western Kansas. Kansas Natural Resources Conference. Manhattan, KS.

**Werdel, T.J.**, A.M. Ricketts, M. Peek, and A.A. Ahlers. **2019**. Assessing factors that shape carnivore diversity in shortgrass prairie ecosystems. American Fisheries Society & The Wildlife Society Joint Annual Conference. Reno, NV.

**Werdel, T.J.**, A.M. Ricketts, M. Peek, and A.A. Ahlers. **2019**. Carnivore richness and diversity is driven by landscape change in shortgrass prairie ecosystems. 99th Annual Meeting of the American Society of Mammalogists. Washington, D.C.

**Werdel, T.J.**, A.M. Ricketts, M. Peek, and A.A. Ahlers. **2019**. Landscape effects on swift fox occupancy in western Kansas. Southwest/Midwest Joint Furbearer Meeting. Enid, OK.

**Werdel, T.J.**, A.M. Ricketts, and A.A. Ahlers. **2019**. Landscape change structures carnivore communities in shortgrass prairie ecosystems. Kansas Natural Resources Conference. Manhattan, KS.

**Werdel, T.J.**, A.M. Ricketts, and A.A. Ahlers. **2018**. Assessing the spatial distribution of swift fox in western Kansas. The Wildlife Society 25th Annual Conference. Cleveland, OH.

**Werdel, T.J.**, J.A. Jenks. **2018**. Survival of bighorn sheep in the Deadwood region of the Black Hills. Nebraska/Central Mountains & Plains Section of The Wildlife Society Annual Meeting. Kearney, NE.

**Werdel, T.J.**, J.A. Jenks, J. Kanta, and C. Lehman. **2016**. Evaluation of the Deadwood bighorn sheep herd translocation. The Wildlife Society 23rd Annual Conference. Raleigh, NC.

**Werdel, T.J.** **2013**. Small mammal population and diversity in relation to prairie dog reintroduction sites. Sevilleta LTER Research Experience for Undergraduates Summer Symposium. Socorro, NM.

\vspace{1\baselineskip}

## *Invited*

**2021** - Texas A&M University, College Station, TX; “Applied Wildlife Management: A Landscape Ecology Approach”

**2021** -	Texas A&M University, College Station, TX; “Traditional Ecological Knowledge: A Place-Based Perspective”

**2021** -	Kansas Department of Wildlife, Parks and Tourism, Emporia, KS; “Distribution of Swift Fox in Kansas”

**2021** -	Kansas State University, Manhattan, KS; “Traditional Ecological Knowledge (TEK) of Wetlands”

**2021** -	Kansas State University, Manhattan, KS; “Bighorn Sheep Capture and Monitoring Techniques”

**2021** -	Kansas State University, Manhattan, KS; “Wild Sheep Natural History”

**2020** -	Kansas State University, Manhattan, KS; “Bighorn Sheep Capture and Monitoring Techniques”

**2019** -	Kansas State University, Manhattan, KS; “Traditional Ecological Knowledge (TEK) of Wetlands”

**2019** -	Wild Sheep Foundation Sheep Show, Reno, NV; “Keynote Speaker: Youth Wildlife Conservation Experience”

**2018** -	The Wildlife Society Annual Conference, Cleveland, OH; “Inclusive Pedagogy Student Panel”

**2018** -	Kansas State University, Manhattan, KS; “Bighorn Sheep Monitoring”

**2018** -	Marlatt Elementary School, Manhattan, KS; “Marlatt STEM Night”

**2018** -	Haskell Indian Nations University, Lawrence, KS; “Initiating a Student Chapter of The Wildlife Society”

**2016** -	Red Cloud Indian School, Pine Ridge, SD; “Toyota STEM Speaker”

**2015** -	South Dakota Game, Fish, and Parks, Rapid City, SD; “Deadwood Bighorn Sheep Translocation”

**2015** -	Kiwanis Club, Lead, SD; “Bighorn Sheep and Community Interaction”

**2015** - Chadron State College, Chadron, NE; “Graduate School Experience and Preparation”

**2013** - Red Cloud Indian School, Pine Ridge, SD; “Project WILD, Children and Wildlife”


\makecvfooter{Curriculum vitae, Ty J. Werdel}{}{}

