---
name: Ty J.
surname: Werdel
position: "Assistant Professor"
address: "Department of Rangeland, Wildlife and Fisheries Management - Texas A&M University, College Station, TX"
profilepic: "headshot_cowboy.jpg"
www: "werdelwildlife.com"
department: "rwfm.tamu.edu/people/werdel-ty/"
email: "ty.werdel@ag.tamu.edu"
github: tywerdel
linkedin: tywerdel
twitter: tywerdel
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 500000
aboutme: "My research interests include the fields of Rangeland and Wildlife Management and Landscape Ecology. This work addresses questions that provide insight into the relationships between wildlife, native environments, and contemporary human-modified landscapes."
docname: CV
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
require(xfun)
packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data structure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative File Paths
             ,'readr'     # Data Loading
             ,'glue'      # String Manipulation
            )
xfun::pkg_attach2(packages, message = FALSE)
source(file = here("","data.R"))
```
```{=tex}
\makecvfooter
  {Dr. Ty J. Werdel~~~·~~~\textit{Curriculum vitae}}
  {\today}
  {\thepage}
```

\thispagestyle{empty}

# Education

```{r EDUCATION}
edu %>%
  detailed_entries(
    with = inst,
    what = degree,
    why = detail,
    when = glue::glue("{endYear}",.na = ""),
    where = where
  )
```
# Certifications

```{r CERTIFICATIONS}
certifications %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```

# Employment

```{r EMPLOYMENT}
work %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )
```


# Publications

## *Peer-Reviewed* (*Werdel Wildlfe Lab Member)

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {\textbf{Werdel, T.J.}, M. Fidino, C.W. Piper, A.M. Ricketts, M.S. Peek, and A.A Ahlers. \textbf{In-Press}. Landscape composition mediates spatiotemporal interactions among sympatric canids in a prairie ecosystem. \textbf{\textit{Ecological Applications}}.}
      \item {Rooney, B., ...,\textbf{T.J. Werdel}, ..., and W.J. McShea (> 100 Co-Authors). \textbf{2025}. SNAPSHOT USA 2019–2023: The first five years of data from a coordinated camera trap survey of the United States. \textbf{\textit{Global Ecology and Biogeography}}. \url{https://doi.org/10.1002/ece3.70488}}
      \item {Whitman, D.\textbf{*} and \textbf{T.J. Werdel}. \textbf{2024}. Occurrence of fox squirrels influenced by fine-scale landscape characteristics on a college campus. \textbf{\textit{Ecology and Evolution}}. \url{https://doi.org/10.1002/ece3.70488}}
      \item {Palomo-Muñoz, G., M. Fidino, \textbf{T.J. Werdel}, C.W. Piper, T. Gallo, M.S. Peek, A.M. Ricketts, and A.A. Ahlers. \textbf{2024}. Mesopredators have differing influences on prey habitat use and diet activity in a multipredator landscape. \textbf{\textit{Ecosphere}}. \url{https://doi.org/10.1002/ecs2.70006}}
      \item {\textbf{Werdel, T.J.}, D. Matarrita-Cascante, and J.E. Lucero. \textbf{2024}. State of traditional ecological knowledge in the wildlife management profession. \textbf{\textit{Journal of Wildlife Management}} (Featured Article). \url{https://doi.org/10.1002/jwmg.22579}}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M.S. Peek, and A.A. Ahlers. \textbf{2023}. Direct and indirect landscape-scale pathways structure carnivore communities in an agro-prairie ecosystem. \textbf{\textit{Journal of Mammalogy}}. \url{https://doi.org/10.1093/jmammal/gyad065}}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks, J.T. Kanta, C.P. Lehman, and T.J. Frink. \textbf{2023}. Resource selection and herbaceous biomass at foraging sites of translocated bighorn sheep. \textbf{\textit{Rangeland Ecology and Management}}. \url{https://doi.org/10.1016/j.rama.2022.12.004}}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M.S. Peek, D.S. Sullins, and A.A. Ahlers. \textbf{2023}. Strategic grassland conservation for swift foxes in multi-use landscapes. \textbf{\textit{Biological Conservation}} (Finalist for TWS Publication Award). \url{https://doi.org/10.1016/j.biocon.2022.109864}}
      \item {Palomo-Muñoz, G., \textbf{T.J. Werdel}, C.W. Piper, M.S. Peek, A.M. Ricketts, and A.A. Ahlers. \textbf{2022}. Spatiotemporal distributions of mammals occurring in an agro-prairie ecosystem. \textbf{\textit{Ecology}}. \url{https://doi.org/10.1002/ecy.3945}}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M.S. Peek, and A.A. Ahlers. \textbf{2022}. Scale-specific landscape effects impose range-limiting constraints on the distribution of swift fox. \textbf{\textit{Landscape Ecology}}, 37(8), 2065--2079. \url{https://doi.org/10.1007/s10980-022-01466-0}}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks, J.T. Kanta, C.P. Lehman, and T.J. Frink. \textbf{2021}. Space use and movement patterns of translocated bighorn sheep. \textbf{\textit{Mammalian Biology}}, 101(3),329--344. \url{https://doi.org/10.1007/s42991-021-00107-4}}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks, T.E. Besser, J.T. Kanta, C.P. Lehman, and T.J. Frink. \textbf{2019}. Restoration of a bighorn sheep population impeded by \textit{Mycoplasma ovipneumoniae} exposure. \textbf{\textit{Restoration Ecology}}, 28(2), 387--395 (Cover Article, Nominated for TWS Publication Award). \url{https://doi.org/https://doi.org/10.1111/rec.13084}}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks, T.E. Besser, J.T. Kanta, C.P. Lehman, and T.J. Frink. \textbf{2018}. Survival of translocated bighorn sheep in the Deadwood region of the Black Hills, South Dakota. \textbf{\textit{Northwestern Naturalist}}, 99(3),222--231. \url{https://doi.org/10.1898/NWN18-06.1}}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

## *Book Chapters*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {Hessami, M.A., \textbf{T.J. Werdel}, S.J. Hoagland, and M.T. Kohl. \textbf{2022}. Melding Past, Present, and Future: The importance of tribal management in wildlife conservation and management. Chapter 1 in C. Bishop, E. Gomez, J. Organ, and T. Ryder eds. \textbf{\textit{Introduction to Wildlife Management and Conservation in North America}}. Great River Learning of Dubuque, IA.}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

## *Book Reviews*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {\textbf{Werdel, T.J.} \textbf{2023}. Wildlife Management and Landscapes: Principles and Applications. \textbf{\textit{Journal of Wildlife Management}}. \url{https://doi.org/10.1002/jwmg.22512}}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

## *In-Revision/Review*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {Piper, C.W., \textbf{T.J. Werdel}, M.S. Peek, A.M. Ricketts, D.S. Sullins, and A.A. Ahlers. \textbf{In-Revision}. Landscape composition and proximity to water structure American badger distributions in shortgrass prairie. \textbf{\textit{Journal of Mammalogy}}.}
      \item {\textbf{Werdel, T.J.}, M. Fidino, C.W. Piper, A.M. Ricketts, M.S. Peek, and A.A Ahlers. \textbf{In-Review}. Landscape composition mediates spatiotemporal interactions among sympatric canids in a prairie ecosystem. \textbf{\textit{Ecological Applications}}.}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

## *Research Coverage in Popular Media*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {\textbf{2024.} Chip Howard's Sports Talk (Campus Squirrels; "May 16, 2024 Hour 2"). \textbf{\textit{Sports Radio 1150 The Zone}.} (\url{https://www.zone1150.com/chip-howard-sports-talk-podcast/})}
      \item {\textbf{2024.} Focus at Four: A{\&}M students study squirrel behavior. \textbf{\textit{KBTX}.} (\url{https://www.kbtx.com/2024/05/12/focus-four-am-students-study-squirrel-behavior/?fbclid=IwZXh0bgNhZW0CMTEAAR2XGXfnp_R-U-YDyr16AQMmBf1aUoPf-45C_18aMnwWeL-Ic3r2SAJ77Ys_aem_AV8Gks9w0tGnZqMjF7L5HG_F-1POM2arX0LlDtu47ggTo4PV0GfAVvL87AHUi-KwDACbwi6gItJ7cx0MBeWycppa})}
      \item {\textbf{2024.} Q{\&}A: TEK AND THE WILDLIFE PROFESSION. \textbf{\textit{The Wildlife Society}.} (\url{https://wildlife.org/qa-tek-and-the-wildlife-profession/?utm_content=290664870&utm_medium=social&utm_source=twitter&hss_channel=tw-26287962})}
      \item {\textbf{2024.} Students Gather Data On Campus Squirrels As Part Of Urban Wildlife Research Effort. \textbf{\textit{Texas A{\&}M TODAY}.} (\url{https://today.tamu.edu/2024/04/24/students-gather-data-on-campus-squirrels-as-part-of-urban-wildlife-research-effort/})}
      \item {\textbf{2024.} Scholarly squirrels: Exploring the dynamics of Texas A{\&}M’s campus wildlife.  \textbf{\textit{AgriLife TODAY}.} (\url{https://agrilifetoday.tamu.edu/2024/04/19/scholarly-squirrels-exploring-the-dynamics-of-texas-ams-campus-wildlife/}) (\url{https://youtu.be/Bperu7Zza3c?si=RNfih9hkZkrok2JL})}
      \item {\textbf{2023.} Texas winters can drive urban squirrels to nest in your home or car. Heres how to keep critters out. \textbf{\textit{Houston Chronicle}.} (\url{https://www.houstonchronicle.com/news/houston-weather/article/squirrels-nesting-cars-homes-texas-winter-18565806.php})}
      \item {\textbf{2021.} Honoring the Land. \textbf{\textit{KSU Ag Report}.} (\url{https://www.k-state.edu/agreport/documents/AgReport_Fall2021_web.pdf})}
      \item {\textbf{2019.} Pneumonia threatens success of bighorn sheep introduction near Deadwood. \textbf{\textit{Rapid City Journal}.} (\url{https://rapidcityjournal.com/news/local/pneumonia-threatens-success-of-bighorn-sheep-introduction-near-deadwood/article_3bb417a2-b9a0-5159-a623-ae334f9672eb.html?utm_medium=social&utm_source=email&utm_campaign=user-share})}
      \item {\textbf{2018.} Life of the wild: Why scientists study ecosystems and the wildlife within them. \textbf{\textit{KSU Seek Research Magazine}.} (\url{https://www.k-state.edu/seek/fall-2018/life-of-the-wild/#prettyPhoto})}
      \item {\textbf{2016.} Hope and Hardship for Black Hills Bighorns. \textbf{\textit{South Dakota Hunting}.} (\url{https://southdakotahunting.com/article/hope-and-hardship-for-black-hills-bighorns})}
      \item {\textbf{2015.} South Dakota Game, Fish {\&} Parks Projects. \textbf{\textit{Ram Tracks}.} (\url{https://www.midwestwildsheep.com/wp-content/uploads/ISSUE-36-2.pdf})}
      \item {\textbf{2015.} New bighorn sheep herd thriving. \textbf{\textit{Black Hills Pioneer}.} (\url{https://www.bhpioneer.com/new-bighorn-sheep-herd-thriving/article_6b6c1d3e-2755-11e5-8f13-231b5dbc0d3d.html?utm_medium=social&utm_source=email&utm_campaign=user-share})}
      \item {\textbf{2015.} SD GETS BIGHORNS TO BOOST NUMBERS. \textbf{\textit{GOHUNT}.} (\url{https://www.gohunt.com/read/south-dakota-uses-canadian-bighorn-sheep-to-boost-numbers#gs.7q5znx})} 
      \item {\textbf{2015.} Deadwood Bighorn Sheep Release. \textbf{\textit{KOTA Territory News}.} (Video on nightly news)} 
      \item {\textbf{2015.} A bighorn sheep herd gets its start near Deadwood. \textbf{\textit{Rapid City Journal}.} (\url{https://rapidcityjournal.com/news/local/a-bighorn-sheep-herd-gets-its-start-near-deadwood/article_7629e423-af84-5c5a-be97-ad9c59c9f0cc.html?utm_medium=social&utm_source=email&utm_campaign=user-share})} 
      \item {\textbf{2015.} New herd of bighorn sheep moved to Hills. \textbf{\textit{Black Hills Pioneer}.} (\url{https://www.bhpioneer.com/local_news/new-herd-of-bighorn-sheep-moved-to-hills/article_808292d8-b3c5-11e4-9b4d-432fad90ac10.html})} 
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}
# Teaching Experience

```{r TEACH}
teach %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```



# Student Mentorship

## *Graduate Student Research Advising* (*Graduated)

```{=tex}
\begin{cvpress}
  \cvpres
    {Autumn Patterson}
    {Ph.D., TAMU RWFM}
    {2025 -- Present}
  \cvpres
    {Reece Allen}
    {Ph.D., TAMU RWFM}
    {2025 -- Present}
  \cvpres
    {Daniel Ramirez}
    {Ph.D., TAMU RWFM}
    {2025 -- Present}
 \cvpres
    {Else Praasterink}
    {M.S., TAMU RWFM}
    {2024 -- Present}
 \cvpres
    {Cade Weiss}
    {M.N.R.D., TAMU RWFM}
    {2024 -- Present} 
 \cvpres
    {Amanda Laboy}
    {M.S., TAMU RWFM}
    {2023 -- Present}
 \cvpres
    {Kayla Art}
    {M.N.R.D., TAMU RWFM}
    {2023 -- Present} 
 \cvpres
    {Lulu Hoffman}
    {M.S., TAMU RWFM}
    {2023 -- Present}
 \cvpres
    {David Pearce}
    {M.S., TAMU RWFM}
    {2023 -- Present}
 \cvpres
    {\textbf{*}Conner Ties}
    {M.S., TAMU RWFM}
    {2022 -- 2024}
\end{cvpress}
```

## *Undergraduate Student Research Advising*

```{=tex}
\begin{cvpress}
 \cvpres
    {Joshua Incardona}
    {B.S., TAMU RWFM}
    {2025 -- Present}
 \cvpres
    {\textbf{*}Daniel Whitman}
    {B.S., Macalester College REU}
    {2023 -- 2024}
 \cvpres
      {\textbf{*}Drake Dancila}
    {B.S., TAMU RWFM}
    {2022 -- 2023}
 \cvpres
    {\textbf{*}Lulu Hoffman}
    {B.S., TAMU RWFM}
    {2022 -- 2023}    
\end{cvpress}
```

## *Secondary School Student Research Advising*

```{=tex}
\begin{cvpress}
 \cvpres
    {\textbf{*}Sebastian Kuo}
    {H.S., Carnegie Vanguard High School}
    {2023 -- 2024}
\end{cvpress}
```


## *Graduate Student Committee Member*

```{=tex}
\begin{cvpress}
 \cvpres
    {Rider Combs}
    {Ph.D., TAMU RWFM}
    {2024 -- Present}
 \cvpres
    {Kylie Perez}
    {Ph.D., TAMU RWFM}
    {2024 -- Present}
 \cvpres
    {Jake Hanes}
    {M.S., TAMU SCSC}
    {2024 -- Present}
 \cvpres
    {\textbf{*}Daniel Ramirez}
    {M.S., TAMU-Kingsville RWM}
    {2023 -- 2024}
\end{cvpress}
```


## *Student Honors & Awards*

```{=tex}
\begin{cvpress}
  \cvpres
    {Avilés-Johnson Fellowship}
    {Autumn Patterson}
    {2025}
  \cvpres
    {Gamma Sigma Delta Outstanding Master’s Student Award}
    {David Pearce}
    {2025}  
  \cvpres
    {RWFM Outstanding Master’s Student of the Year Award}
    {David Pearce}
    {2025}  
  \cvpres
    {TAMU Student Research Week Outstanding Poster Presentation}
    {Kayla Art}
    {2025}
  \cvpres
    {TAMU Student Research Week Outstanding Oral Presentation}
    {David Pearce}
    {2025}
  \cvpres
    {RWFM Spring Graduate Student Travel Grant}
    {Amanda Laboy}
    {2025}
  \cvpres
    {RWFM Spring Graduate Student Travel Grant}
    {Kayla Art}
    {2025}
  \cvpres
    {RWFM Spring Graduate Student Travel Grant}
    {David Pearce}
    {2025}
  \cvpres
    {RWFM Spring Graduate Student Travel Grant}
    {Lulu Hoffman}
    {2025}
  \cvpres
    {RWFM Fall Graduate Student Travel Grant}
    {David Pearce}
    {2024}
  \cvpres
    {RWFM Fall Graduate Student Travel Grant}
    {Conner Ties}
    {2024}
  \cvpres
    {Houston Safari Club Foundation Dan L. Duncan Scholarship}
    {Conner Ties}
    {2024}
  \cvpres
    {Houston Safari Club Foundation Dan L. Duncan Scholarship}
    {David Pearce}
    {2024}
  \cvpres
    {TAMU GPS Graduate Student Research and Presentation Travel Award}
    {Lulu Hoffman}
    {2024}
  \cvpres
    {RWFM Summer Graduate Student Travel Grant (x2)}
    {David Pearce}
    {2024}
  \cvpres
    {RWFM Summer Graduate Student Travel Grant}
    {Amanda Laboy}
    {2024}
  \cvpres
    {RWFM Summer Graduate Student Travel Grant}
    {Lulu Hoffman}
    {2024}
  \cvpres
    {RWFM Outstanding Master’s Student of the Year Award}
    {Conner Ties}
    {2024}
  \cvpres
    {American Society of Mammalogists Student Travel Award}
    {David Pearce}
    {2024}
  \cvpres
    {AgGIE Leadership Community Student Development Grant}
    {Amanda Laboy}
    {2024}
  \cvpres
    {RWFM Spring Graduate Student Travel Grant}
    {David Pearce}
    {2024}
 \cvpres
    {RWFM Spring Graduate Student Travel Grant}
    {Conner Ties}
    {2024}
 \cvpres
    {COALS Merit Fellowship}
    {Amanda Laboy}
    {2023}
 \cvpres
    {RWFM Graduate Student Travel Grant}
    {Conner Ties}
    {2023}
  \cvpres
    {RWFM Graduate Student Travel Grant}
    {David Pearce}
    {2023}
 \cvpres
    {RWFM Outstanding Undergraduate Student of the Year Award}
    {Drake Dancila}
    {2023}
  \cvpres
    {RWFM Outstanding Undergraduate Student of the Year Award}
    {Lulu Hoffman}
    {2023}
\end{cvpress}

```

# Investigator Grants & Contracts

## *Funded (Total: $4,111,869, Lab Allocated: $481,124)*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {\textbf{Luminant Environmental Research Program}. 2024-2027. Ecological impact of varying vegetation management strategies employed on solar farms. \textbf{\$227,644; \textit{Funded}}. PI: Stacy Hines, Co-PIs: \textbf{Ty J. Werdel (Lab Allocated: \$45,529)}, Nuria Gomez-Casanovas, Morgan Treadwell, and Humberto Perotto.}
      \item {\textbf{TAMU AgriLife Research Rangeland Ecology and Management Research Funding}. 2024-2026. Developing proxies for rangeland assessments using drones. \textbf{\$106,700; \textit{Funded}}. PI: Humberto Perotto, Co-PIs: Sorin Popescu, \textbf{Ty J. Werdel (Lab Allocated: \$17,783)}, Jacob Lucero, Jeff Goodwin, and Morgan Treadwell.}
      \item {\textbf{TAMU AgriLife Research Rangeland Ecology and Management Research Funding}. 2024-2026. Working towards healthy rangelands: understanding the factors limiting the adoption of grazing, fire, and wildfire management practices among exurban landowners. \textbf{\$106,448; \textit{Funded}}. PI: David  Matarrita, Co-PIs: Rafael Landeverde, \textbf{Ty J. Werdel (Lab Allocated: \$26,612)}, and Morgan Treadwell.}
      \item {\textbf{TAMU AgriLife Research Animal Health and Disease Research Capacity Funding}. 2024-2025. The impact of osmotic stress on the catfish pathogen \textit{Aeromonas hydrophila}: Implications for managing motile \textit{Aeromonas} septicemia (MAS) in U.S. catfish farming. \textbf{\$100,000; \textit{Funded}}. PI: Haitham Mohammed, Co-PI: \textbf{Ty J. Werdel (Lab Allocated: \$50,000)}.}
      \item {\textbf{Private Donation}. 2023. Student-led population ecology of fox squirrels on the TAMU campus. \textbf{\$10,000; \textit{Funded}}. PI: \textbf{Ty J. Werdel}.}
      \item {\textbf{USFWS}. 2023-2027. Evaluation and mitigation for sensitive state threatened and endangered wildlife.
\textbf{\$3,399,877; \textit{Funded}}. Co-PIs: Marcus Blum, Paul Crump, Jacob Dykes, Whitney Gann, Andrew Gregory, Toby Hibbitts, Mathew Kramm, Roel Lopez, Kevin Moczygemba, Michael Morrison, Humberto Perotto, Wady Ryberg, Danielle Walkup, Stephen Webb, and \textbf{Ty J. Werdel (Lab Allocated: \$170,000)}.}
      \item {\textbf{Department of Rangeland, Wildlife and Fisheries Management}. 2023-2024. Long-term wildlife monitoring for unmanaged rangelands transitioning to planned grazing management. \textbf{\$100,000; \textit{Funded}}. PIs: Stephen L. Webb and \textbf{Ty J. Werdel}.}
      \item {\textbf{Private Donation}. 2023. Long-term wildlife monitoring for unmanaged rangelands transitioning to planned grazing management. \textbf{\$1,200; \textit{Funded}}. PI: \textbf{Ty J. Werdel}.}
      \item {\textbf{Department of Rangeland, Wildlife and Fisheries Management}. 2023-2025. River otter (\textit{Lontra canadensis}) population dynamics in Texas. \textbf{\$60,000; \textit{Funded}}. PI: \textbf{Ty J. Werdel}.}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

## *Unfunded Proposals*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {\textbf{TAMU AgriLife Research Rangeland Ecology and Management Research Funding}. 2024-2026. Resource selection and spatial interactions of native, exotic, and domestic ungulates on Texas rangelands. \textbf{\$150,000; \textit{Not Funded}}. PI: \textbf{Ty J. Werdel}, Co-PIs: Jacob E. Lucero, Humberto Perotto, and Jacob L. Dykes.}
      \item {\textbf{National Science Foundation}. 2023-2025. Incorporating Native American partnerships and knowledge into Great Plains fire science. \textbf{\$199,404; \textit{Not Funded}}. PI: David  Matarrita, Co-PIs: Bradford Wilcox  and \textbf{Ty J. Werdel}.}
      \item {\textbf{USDA APHIS Wildlife Services}. 2023-2024. Spatial interactions and potential disease transmission of free-ranging native and exotic ungulates. \textbf{\$225,437; \textit{Not Funded}}. PI: \textbf{Ty J. Werdel}.}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

# Honors & Awards

## *Awards ($121,150)*

```{=tex}
\begin{cvpress}
 \cvpres
    {Community Building Through Mentorship Conference Panel Travel Grant}
    {The Wildlife Society}
    {2022}
 \cvpres
    {Agriculture Dean and Director’s Award for Graduate Student Research}
    {Kansas State University}
    {2022}
 \cvpres
    {Advancing Agricultural Science Opportunities for Native Americans Scholarship}
    {AISES}
    {2021}
 \cvpres
    {Robert Nunemacher Scholarship}
    {Kansas State University}
    {2021}
 \cvpres
    {Advancing Agricultural Science Opportunities for Native Americans Research Award}
    {AISES}
    {2020}
 \cvpres
    {Advancing Agricultural Science Opportunities for Native Americans Scholarship}
    {AISES}
    {2020}
 \cvpres
    {Lighting the Pathway to Faculty Careers for Natives in STEM}
    {AISES}
    {2020}
 \cvpres
    {College of Agriculture Graduate Student Recognition of Achievement}
    {Kansas State University}
    {2020}
 \cvpres
    {AISES Together Towards Tomorrow T3 Scholarship}
    {AISES}
    {2020}
 \cvpres
    {Gamma Sigma Delta}
    {Kansas State University}
    {2019}
 \cvpres
    {AISES Travel Grant}
    {AISES}
    {2019}
 \cvpres
    {Advancing Agricultural Science Opportunities for Native Americans Scholarship}
    {AISES}
    {2019}
 \cvpres
    {Kansas State University Graduate Student Recognition of Achievement}
    {Kansas State University}
    {2019}
 \cvpres
    {College of Agriculture Graduate Student Recognition of Achievement}
    {Kansas State University}
    {2019}
 \cvpres
    {Inclusive Pedagogy Travel Grant}
    {The Wildlife Society}
    {2018}
 \cvpres
    {Life Membership Fund Scholarship}
    {Wild Sheep Foundation}
    {2018}
 \cvpres
    {Predoctoral Ford Fellowship}
    {(Honorable Mention) Ford Foundation Fellowships Program}
    {2018}
 \cvpres
    {Native Student Professional Development Grant}
    {The Wildlife Society}
    {2017}
 \cvpres
    {Launch Collegiate Business Pitch Competition}
    {Kansas State University}
    {2017}
 \cvpres
    {Native Student Professional Development Grant}
    {The Wildlife Society}
    {2016}
 \cvpres
    {Phi Kappa Phi Honor Society}
    {South Dakota State University}
    {2016}
 \cvpres
    {Excellence in Wildlife Management}
    {Chadron State College}
    {2013}
 \cvpres
    {Platinum Eagle Award}
    {(Finalist) Chadron State College}
    {2013}
 \cvpres
    {Gates Millennium Scholarship}
    {Bill and Melinda Gates Foundation}
    {2005}
 \cvpres
    {Scholastic Excellence in Engineering}
    {University of Wyoming}
    {2005}
 \cvpres
    {Scholars Stipend}
    {University of Wyoming}
    {2005}
 \cvpres
    {Computer Science, Engineering, and Mathematics Scholarship}
    {University of Wyoming}
    {2005}
 \cvpres
    {Honors Program}
    {University of Wyoming}
    {2005}
\end{cvpress}

```


# Professional Service

## *Executive Service in Professional Organizations*


```{r SERVICE}
service %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )
```

\vspace{1\baselineskip}

## *Working Group Membership*

```{=tex}
\begin{cvpress}
 \cvpres
  {Colleges and Universities Education Working Group}
  {The Wildlife Society}
  {2024 -- Present}
 \cvpres
  {Rangeland Wildlife Working Group}
  {The Wildlife Society}
  {2018 -- Present}
 \cvpres
    {Native Peoples' Wildlife Management Working Group}
    {The Wildlife Society}
    {2015 -- Present}
 \cvpres
    {Student Development Working Group}
    {The Wildlife Society}
    {2013 -- 2022}
\end{cvpress}
```

\vspace{1\baselineskip}

## *Chapter Membership*

```{=tex}
\begin{cvpress}
 \cvpres
    {Southwest Section}
    {The Wildlife Society}
    {2023 -- Present}
 \cvpres
    {Texas Chapter}
    {The Wildlife Society}
    {2023 -- Present}
 \cvpres
    {Central Mountains and Plains Section}
    {The Wildlife Society}
    {2018 -- 2022}
 \cvpres
    {Kansas Chapter}
    {The Wildlife Society}
    {2017 -- 2022}
 \cvpres
    {South Dakota Chapter}
    {The Wildlife Society}
    {2014 -- 2017}
 \cvpres
    {Nebraska Chapter}
    {The Wildlife Society}
    {2013 -- 2014}
 \cvpres
    {Chadron State Student Chapter}
    {The Wildlife Society}
    {2012 -- 2013}
\end{cvpress}
```

\vspace{1\baselineskip}

## *Professional Organization Membership*

```{=tex}
\begin{cvmemb}
 \cvmem
    {Society for Range Management}
    {}
    {2023 -- Present}
 \cvmem
    {Society for Advancement of Chicanos/Hispanics and Native Americans in Science}
    {}
    {2021 -- Present}
 \cvmem
    {Gamma Sigma Delta Honor Society}
    {}
    {2019 -- Present}
 \cvmem
    {American Indian Science and Engineering Society}
    {}
    {2019 -- Present}
 \cvmem
    {Swift Fox Conservation Team}
    {}
    {2018 -- Present}
 \cvmem
    {Phi Kappa Phi Honor Society}
    {}
    {2016 -- Present}
 \cvmem
    {Native American Fish and Wildlife Society}
    {}
    {2015 -- Present}
 \cvmem
    {Rocky Mountain Bighorn Society}
    {}
    {2015 -- 2017}
 \cvmem
    {Wild Sheep Foundation}
    {}
    {2014 -- 2020}
 \cvmem
    {American Society of Mammalogists}
    {}
    {2013 -- Present}
 \cvmem
    {The Wildlife Society}
    {}
    {2013 -- Present}
\end{cvmemb}
```

\vspace{1\baselineskip}

## *External Journal Reviewer (13)*
```{=tex}
\begin{cvmemb}
 \cvmem
    {Ecological Applications}
    {}
    {2025}
 \cvmem
    {The Journal of Wildlife Management}
    {(3)}
    {2023 (x2), 2025}
 \cvmem
    {Ecology and Evolution}
    {}
    {2024}
 \cvmem
    {Movement Ecology}
    {}
    {2024}

 \cvmem
    {Journal of Fish and Wildlife Management}
    {}
    {2023}
 \cvmem
    {PeerJ}
    {(2)}
    {2022, 2023}
 \cvmem
    {Frontiers in Ecology and the Environment}
    {}
    {2023}
 \cvmem
    {Science}
    {}
    {2023}
 \cvmem
    {Canadian Journal of Zoology}
    {}
    {2022}
 \cvmem
    {Journal of Mammalogy}
    {}
    {2021}
\end{cvmemb}
```


\vspace{1\baselineskip}

# University Service

## *Texas A&M University*

```{=tex}
\begin{cvpress}
 \cvpres
    {Poster Presentation Judge}
    {COALS Research Symposium}
    {2024} 
 \cvpres
    {Faculty Reviewer}
    {Avilés-Johnson Fellowship Program}
    {2024} 
 \cvpres
    {Faculty Advisor}
    {TAMU Student Chapter of The Wildlife Society}
    {2023 -- Present}
\end{cvpress}
```

\vspace{1\baselineskip}

## *Department*

```{=tex}
\begin{cvpress}
 \cvpres
    {Outdoor Enterprise Management Search Committee}
    {RWFM}
    {2024 -- Present}
 \cvpres
    {Graduate Student Space Assignment Committee}
    {RWFM}
    {2024}
 \cvpres
    {Outdoor Enterprise Management Curriculum Committee}
    {RWFM}
    {2023 -- Present}
 \cvpres
    {Awards Committee}
    {RWFM}
    {2023 -- Present}
 \cvpres
    {Undergraduate Committee}
    {RWFM}
    {2023 -- Present}  
 \cvpres
    {Caesar Kleberg Chair Search Committee}
    {RWFM}
    {2023 -- 2024}
\end{cvpress}
```

\vspace{1\baselineskip}

# Presentations

## *Contributed* (*Werdel Wildlfe Lab Member)
\vspace{1\baselineskip}
```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {Art, K.\textbf{*} and \textbf{T.J. Werdel}. \textbf{2025}. How flight behavior responses of eastern fox squirrels differ between rural and synurbanized populations in College Station, Texas. \textbf{\textit{TAMU Student Research Week, College Station, TX}}.}          
      \item {Pearce, D.L.\textbf{*}, T. Schafer, H. Perotto-Baldivieso, M.E. Blum, \textbf{T.J. Werdel}, and S. Webb. \textbf{2025}. How many deer live in the brush? Comparing camera and helicopter survey and modeling methods to estimate white-tailed deer abundance in south Texas. \textbf{\textit{TAMU Student Research Week, College Station, TX}}.}    
      \item {Pearce, D.L.\textbf{*}, T. Schafer, H. Perotto-Baldivieso, \textbf{T.J. Werdel}, and S. Webb. \textbf{2025}. Song of the South: Estimating northern bobwhite quail abundance using passive acoustic monitors. \textbf{\textit{Ecological Integration Symposium, College Station, TX}}.}    
      \item {Erdogan, O., M.I. Haque, H.A. Biswas, \textbf{T.J. Werdel}, and H. Mohammed. \textbf{2025}. Exploring the impact of osmotic stress on virulent \textit{Aeromonas hydrophila}, the causative agent of motile \textit{Aeromonas septicemia} (MAS) in U.S. catfish aquaculture. \textbf{\textit{Aquaculture 2025, New Orleans, LA}}.}
      \item {Hoffman, M.G.\textbf{*}, \textbf{T.J. Werdel}, J. Dykes, H.L. Perotto, and W. Cook. \textbf{2025}. Spatial interactions of axis and white-tailed deer in the Edwards Plateau Ecoregion of Texas. \textbf{\textit{Texas Chapter of The Wildlife Society Annual Conference, Denton, TX}}.}
      \item {Pearce, D.L.\textbf{*}, T. Schafer, H. Perotto-Baldivieso, \textbf{T.J. Werdel}, and S. Webb. \textbf{2025}. Did you hear that? Counting quail Using autonomous recorders and hierarchical models. \textbf{\textit{Texas Chapter of The Wildlife Society Annual Conference, Denton, TX}}.}      
      \item {Art, K.\textbf{*} and \textbf{T.J. Werdel}. \textbf{2025}. How flight behavior responses of eastern fox squirrels differ between rural and synurbanized populations in College Station, Texas. \textbf{\textit{Texas Chapter of The Wildlife Society Annual Conference, Denton, TX}}.}      
      \item {Ramirez, D.\textbf{*}, S. Hines, \textbf{T.J. Werdel}, N. Gomez-Casanovas, M. Treadwell and H. Perotto-Baldivieso. \textbf{2025}. Ecological impact of varying vegetation management strategies employed on solar rarms. \textbf{\textit{Texas Chapter of The Wildlife Society Annual Conference, Denton, TX}}.}
      \item {Erdogan, O., M.I. Haque, H.A. Biswas, \textbf{T.J. Werdel}, and H. Mohammed. \textbf{2025}. Growth dynamics, morphological adaptation, biofilm formation, and virulence of \textit{Aeromonas hydrophila} in response to osmotic stress. \textbf{\textit{48th Annual Eastern Fish Health Workshop, Grand Rapids, MI}}.}
      \item {Erdogan, O., M.I. Haque, H.A. Biswas, \textbf{T.J. Werdel}, and H. Mohammed. \textbf{2025}. An investigation of the osmotic effects on \textit{Aeromonas hydrophila}, the causative agent of motile \textit{Aeromonas} septicemia. \textbf{\textit{Texas Aquaculture Association Annual Meeting, Port Lavaca, TX}}.}
      \item {Ties, C.\textbf{*}, \textbf{T.J. Werdel}, and S. Webb. \textbf{2024}. Where have they all gone? Swift fox in Texas. \textbf{\textit{The Wildlife Society 31st Annual Conference, Baltimore, MD}}.}
      \item {Pearce, D.L.\textbf{*}, T. Schafer, H. Perotto-Baldivieso, \textbf{T.J. Werdel}, and S. Webb. \textbf{2024}. Comparing camera, helicopter, and drone surveys to estimate white-tailed deer \textit{(Odocoileus virginianus)} abundance. \textbf{\textit{The Wildlife Society 31st Annual Conference, Baltimore, MD}}.}
      \item {Pearce, D.L.\textbf{*} and \textbf{T.J. Werdel}. \textbf{2024}. Tails on the Great Plains: Interspecific interactions between two cervids in western Kansas. \textbf{\textit{103rd Annual Meeting of the American Society of Mammalogists, Boulder, CO}}.}
      \item {Laboy, A.\textbf{*}, R. Lopez, and \textbf{T.J. Werdel}. \textbf{2024}. Evaluating small mammal biodiversity using camera traps. \textbf{\textit{103rd Annual Meeting of the American Society of Mammalogists, Boulder, CO}}.}
      \item {Hoffman, M.G.\textbf{*}, W.E. Cook, H.L. Perotto, and \textbf{T.J. Werdel}. \textbf{2024}. Spatial interactions of axis and white-tailed deer in the Texas hill country. \textbf{\textit{103rd Annual Meeting of the American Society of Mammalogists, Boulder, CO}}.}
      \item {Laboy, A.\textbf{*}, R. Lopez, and \textbf{T.J. Werdel}. \textbf{2024}. Evaluating small mammal biodiversity using camera traps. \textbf{\textit{Ecological Integration Symposium, College Station, TX}}.}
      \item {Laboy, A.\textbf{*}, R. Lopez, and \textbf{T.J. Werdel}. \textbf{2024}. Evaluating small mammal biodiversity using camera traps. \textbf{\textit{Diversity in Science Symposium, College Station, TX}}.}
      \item {Laboy, A.\textbf{*}, R. Lopez, and \textbf{T.J. Werdel}. \textbf{2024}. Evaluating small mammal biodiversity using camera traps. \textbf{\textit{TAMU Student Research Week, College Station, TX}}.}
      \item {Perez, K., H.L. Perotto, D. Bernal, S. Popescu, \textbf{T.J. Werdel}, J. Lucero, J. Goodwin, and M. Treadwell. \textbf{2024}. Leveraging drone technology for rangeland ecology and management. \textbf{\textit{Texas Section of the Society for Range Management Annual Symposium, Victoria, TX}}.}
      \item {Ramirez, D.\textbf{*}, S. Hines, \textbf{T.J. Werdel}, N. Gomez-Casanova, M. Treadwell, and H. Perotto. \textbf{2024}. Ecological and economic impact of varying vegetation management strategies employed on solar farms. \textbf{\textit{Texas A{\&}M AgriLife Research and Extension Corpus Christi 50th Anniversary, Corpus Christi, TX}}.}
      \item {\textbf{Werdel, T.J.}, D. Matarrita-Cascante, and J.E. Lucero. \textbf{2024}. State of traditional ecological knowledge in the wildlife management profession. \textbf{\textit{Texas Chapter of The Wildlife Society Annual Conference, Houston, TX}}.}
      \item {Ties, C.\textbf{*}, S.L. Webb, and \textbf{T.J. Werdel}. \textbf{2024}. Mapping collared peccary habitat: species distribution modeling in the South Texas Plains and Trans-Pecos ecoregions. \textbf{\textit{Texas Chapter of The Wildlife Society Annual Conference, Houston, TX}}.}
      \item {Palomo-Muñoz, G., \textbf{T.J. Werdel}, C.W. Piper, M. Fidino, T. Gallo, M.S. Peek, A.M. Ricketts, and A.A. Ahlers. \textbf{2024}. Habitat use by black-tailed jackrabbits and eastern cottontail rabbits in a multipredator landscape. \textbf{\textit{Kansas Natural Resources Conference, Manhattan, KS}}.}
      \item {Ties, C.\textbf{*}, S.L. Webb, and \textbf{T.J. Werdel}. \textbf{2023}. Using community science to determine collared peccary spatial distribution in Texas. \textbf{\textit{The Wildlife Society 30th Annual Conference, Louisville, KY}}.}
      \item {Ties, C.\textbf{*}, S.L. Webb, and \textbf{T.J. Werdel}. \textbf{2023}. Mapping collared peccary habitat: species distribution modeling in the south Texas plains. \textbf{\textit{Texas Section Society For Range Management, Bastrop, TX}}.}
      \item {Whitman, D.\textbf{*} and \textbf{T.J. Werdel}. \textbf{2023}. Campus fox squirrel presence influenced by fine-scale landscape characteristics. \textbf{\textit{Macalester College Summer Showcase, Saint Paul, MN}}.}
      \item {Dancila, A.D.\textbf{*}, \textbf{T.J. Werdel}, S.M. Chinn, J.C. Beasley, and S.L. Webb. \textbf{2023}. Analysis of reproductive parameters of wild pigs in southcentral Oklahoma. \textbf{\textit{RWFM Convocation, College Station, TX}}.}
      \item {Hoffman, M.G.\textbf{*}, M.D. Proctor, \textbf{T.J. Werdel}, and S.L. Webb. \textbf{2023}. Activity patterns and potential interactions among cattle, white-tailed deer, and wild pigs. \textbf{\textit{RWFM Convocation, College Station, TX}}.}
      \item {Whitman, D.\textbf{*} and \textbf{T.J. Werdel.}. \textbf{2023}. Fine-scale landscape features influence fox squirrel presence on urban campus. \textbf{\textit{LAUNCH Summer Undergraduate Research Symposium, College Station, TX}}.}
      \item {Whitman, D.\textbf{*} and \textbf{T.J. Werdel}. \textbf{2023}. Campus fox squirrel presence influenced by fine-scale landscape characteristics. \textbf{\textit{College of Agriculture and Life Sciences Summer Undergraduate Research Symposium, College Station, TX}}.}
      \item {Hoffman, M.G.\textbf{*}, \textbf{T.J. Werdel}, M.D. Proctor, and S.L. Webb. \textbf{2023}. Activity patterns and potential interactions among cattle, white-tailed deer, and wild pigs. \textbf{\textit{Ecological Integration Symposium, College Station, TX}}.}
      \item {Dancila, A.D.\textbf{*}, \textbf{T.J. Werdel}, S.M. Chinn, J.C. Beasley, and S.L. Webb. \textbf{2023}. Analysis of reproductive parameters of wild pigs in southcentral Oklahoma. \textbf{\textit{TAMU Student Research Week, College Station, TX}}.}
      \item {Hoffman, M.G.\textbf{*}, M.D. Proctor, \textbf{T.J. Werdel}, and S.L. Webb. \textbf{2023}. Activity patterns and potential interactions among cattle, white-tailed deer, and wild pigs. \textbf{\textit{TAMU Student Research Week, College Station, TX}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M.S. Peek, D.S. Sullins, and A.A. Ahlers. \textbf{2023}. Strategic grassland conservation for swift foxes in multi-use landscapes. \textbf{\textit{Texas Chapter of The Wildlife Society Annual Conference, Houston, TX}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, M.S. Peek, A.M. Ricketts, and A.A. Ahlers. \textbf{2023}. Landscape-scale effects structure carnivore communities in an agro-prairie ecosystem. \textbf{\textit{Kansas Natural Resources Conference, Manhattan, KS}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, M.S. Peek, A.M. Ricketts, D.S. Sullins, and A.A. Ahlers. \textbf{2023}. Strategic grassland conservation for swift foxes in multi-use landscapes. \textbf{\textit{Kansas Natural Resources Conference, Manhattan, KS}}.}
      \item {Palomo-Muñoz, G., \textbf{T.J. Werdel}, C.W. Piper, M. Fidno, A.M. Ricketts, and A.A. Ahlers. \textbf{2022}. Local-scale habitat structure mediates interactions between coyotes and lagamorphs. \textbf{\textit{101st Annual Meeting of the American Society of Mammalogists, Tucson, AZ}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2021}. Scale-specific landscape effects impose range-limiting constraints on the distribution of swift foxes. \textbf{\textit{The Wildlife Society 28th Annual Conference, Virtual}}.}
      \item {Piper, C.W, \textbf{T.J. Werdel}, A.M. Ricketts, D. Sullins, M. Peek, and A.A. Ahlers. \textbf{2021}. Landscape composition and proximity to water structure American badger distributions in shortgrass prairies. \textbf{\textit{The Wildlife Society 28th Annual Conference, Virtual}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2021}. Multiscale landscape effects impose range-limiting constraints on the distribution of swift fox. \textbf{\textit{Swift Fox Conservation Team Meeting, Virtual}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2021}. Multiscale landscape effects impose range-limiting constraints on the distribution of swift fox. \textbf{\textit{Midwest Association of Fish and Wildlife Agencies Furbearer Workshop, Virtual}}.}
      \item {Piper, C.W, \textbf{T.J. Werdel}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2021}. Landscape composition and proximity to water structure American badger (\textit{Taxidea taxus}) distributions in shortgrass prairies. \textbf{\textit{Midwest Association of Fish and Wildlife Agencies Furbearer Workshop, Virtual}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2020}. Assessing factors that influence occupancy and colonization of swift fox in western Kansas. \textbf{\textit{Kansas Natural Resources Conference, Manhattan, KS}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2019}. Assessing factors that shape carnivore diversity in shortgrass prairie ecosystems. \textbf{\textit{American Fisheries Society and The Wildlife Society 2019 Joint Annual Conference, Reno, NV}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2019}. Carnivore richness and diversity is driven by landscape change in shortgrass prairie ecosystems. \textbf{\textit{99th Annual Meeting of the American Society of Mammalogists, Washington, D.C}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2019}. Landscape effects on swift fox occupancy in western Kansas. \textbf{\textit{Southwest/Midwest Joint Furbearer Meeting, Enid, OK}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, and A.A. Ahlers. \textbf{2019}. Landscape change structures carnivore communities in shortgrass prairie ecosystems. \textbf{\textit{Kansas Natural Resources Conference, Manhattan, KS}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2018}. Assessing the spatial distribution of swift fox in western Kansas. \textbf{\textit{The Wildlife Society 25th Annual Conference, Cleveland, OH}}.}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks. \textbf{2018}. Survival of bighorn sheep in the Deadwood region of the Black Hills. \textbf{\textit{Nebraska/Central Mountains and Plains Section of The Wildlife Society Annual Meeting, Kearney, NE}}.}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks, J. Kanta, and C. Lehman. \textbf{2016}. Evaluation of the Deadwood bighorn sheep herd translocation. \textbf{\textit{The Wildlife Society 23rd Annual Conference, Raleigh, NC}}.}
      \item {\textbf{Werdel, T.J.}. \textbf{2013}. Small mammal population and diversity in relation to prairie dog reintroduction sites. \textbf{\textit{Sevilleta LTER Research Experience for Undergraduates Summer Symposium, Socorro, NM}}.}
      \end{cvetar}
    }
\end{cvpubs}
```



\vspace{1\baselineskip}
## *Invited*

```{r INVITED}
invited %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```


\vspace{1\baselineskip}
## *Guest Lectures*

```{r GUEST}
guest %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```