---
name: Ty J.
surname: Werdel
position: "Assistant Professor"
address: "Department of Rangeland, Wildlife and Fisheries Management - Texas A&M University, College Station, TX"
profilepic: "headshot_cowboy.jpg"
www: "werdelwildlife.com"
department: "rwfm.tamu.edu/people/werdel-ty/"
email: "ty.werdel@ag.tamu.edu"
github: tywerdel
linkedin: tywerdel
twitter: tywerdel
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 500000
aboutme: "My research interests include the fields of Rangeland and Wildlife Management and Landscape Ecology. This work addresses questions that provide insight into the relationships between wildlife, native environments, and contemporary human-modified landscapes."
docname: CV
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
require(xfun)
packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data structure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative File Paths
             ,'readr'     # Data Loading
             ,'glue'      # String Manipulation
            )
xfun::pkg_attach2(packages, message = FALSE)
source(file = here("","data.R"))
```
```{=tex}
\makecvfooter
  {Dr. Ty J. Werdel~~~·~~~\textit{Curriculum vitae}}
  {\today}
  {\thepage}
```

\thispagestyle{empty}

# Education

```{r EDUCATION}
edu %>%
  detailed_entries(
    with = inst,
    what = degree,
    why = detail,
    when = glue::glue("{endYear}",.na = ""),
    where = where
  )
```
# Certifications

```{r CERTIFICATIONS}
certifications %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```

# Employment

```{r EMPLOYMENT}
work %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )
```


# Publications

## *Peer-Reviewed*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {\textbf{Werdel, T.J.}, D. Matarrita-Cascante, and J.E. Lucero. \textbf{2024}. State of traditional ecological knowledge in the wildlife management profession. \textbf{\textit{Journal of Wildlife Management}}. \url{https://doi.org/10.1002/jwmg.22579}}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M.S. Peek, and A.A. Ahlers. \textbf{2023}. Direct and indirect landscape-scale pathways structure carnivore communities in an agro-prairie ecosystem. \textbf{\textit{Journal of Mammalogy}}. \url{https://doi.org/10.1093/jmammal/gyad065}}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks, J.T. Kanta, C.P. Lehman, and T.J. Frink. \textbf{2023}. Resource selection and herbaceous biomass at foraging sites of translocated bighorn sheep. \textbf{\textit{Rangeland Ecology and Management}}. \url{https://doi.org/10.1016/j.rama.2022.12.004}}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M.S. Peek, D.S. Sullins, and A.A. Ahlers. \textbf{2023}. Strategic grassland conservation for swift foxes in multi-use landscapes. \textbf{\textit{Biological Conservation}}. \url{https://doi.org/10.1016/j.biocon.2022.109864}}
      \item {Palomo-Muñoz, G, \textbf{T.J. Werdel}, C.W. Piper, M.S. Peek, A.M. Ricketts, and A.A. Ahlers. \textbf{2022}. Spatiotemporal distributions of mammals occurring in an agro-prairie ecosystem. \textbf{\textit{Ecology}}. \url{https://doi.org/10.1002/ecy.3945}}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M.S. Peek, and A.A. Ahlers. \textbf{2022}. Scale-specific landscape effects impose range-limiting constraints on the distribution of swift fox. \textbf{\textit{Landscape Ecology}}, 37(8), 2065--2079. \url{https://doi.org/10.1007/s10980-022-01466-0}}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks, J.T. Kanta, C.P. Lehman, and T.J. Frink. \textbf{2021}. Space use and movement patterns of translocated bighorn sheep. \textbf{\textit{Mammalian Biology}}, 101(3),329--344. \url{https://doi.org/10.1007/s42991-021-00107-4}}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks, T.E. Besser, J.T. Kanta, C.P. Lehman, and T.J. Frink. \textbf{2019}. Restoration of a bighorn sheep population impeded by \textit{Mycoplasma ovipneumoniae} exposure. \textbf{\textit{Restoration Ecology}}, 28(2), 387--395 (Cover Article). \url{https://doi.org/https://doi.org/10.1111/rec.13084}}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks, T.E. Besser, J.T. Kanta, C.P. Lehman, and T.J. Frink. \textbf{2018}. Survival of translocated bighorn sheep in the Deadwood region of the Black Hills, South Dakota. \textbf{\textit{Northwestern Naturalist}}, 99(3),222--231. \url{https://doi.org/10.1898/NWN18-06.1}}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

## *Book Chapters*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {Hessami, M.A., \textbf{T.J. Werdel}, S.J. Hoagland, and M.T. Kohl. \textbf{2022}. Melding Past, Present, and Future: The importance of tribal management in wildlife conservation and management. Chapter 1 in C. Bishop, E. Gomez, J. Organ, and T. Ryder eds. \textbf{\textit{Introduction to Wildlife Management and Conservation in North America}}. Great River Learning of Dubuque, IA.}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

## *Book Reviews*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {\textbf{Werdel, T.J.} \textbf{2023}. Wildlife Management and Landscapes: Principles and Applications. \textbf{\textit{Journal of Wildlife Management}}. \url{https://doi.org/10.1002/jwmg.22512}}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

## *In-Revision/Review*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {Piper, C.W., \textbf{T.J. Werdel}, M.S. Peek, A.M. Ricketts, D.S. Sullins, and A.A. Ahlers. \textbf{In-Revision}. Landscape composition and proximity to water structure American badger distributions in shortgrass prairie. \textbf{\textit{Journal of Mammalogy}}.}
      \item {\textbf{Werdel, T.J.}, M. Fidino, C.W. Piper, A.M. Ricketts, M.S. Peek, and A.A Ahlers. \textbf{In-Revision}. Landscape composition mediates spatiotemporal interactions among sympatric canids in a prairie ecosystem. \textbf{\textit{Ecological Applications}}.}
      \item {Palomo-Muñoz, G., M. Fidino \textbf{T.J. Werdel}, C.W. Piper, T. Gallo, M.S. Peek, A.M. Ricketts, and A.A. Ahlers. \textbf{In-Revision}. Mesopredators have differing influences on prey habitat use and diet activity in a multipredator landscape. \textbf{\textit{Ecosphere}}.}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}
# Teaching Experience

```{r TEACH}
teach %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```



# Student Mentorship

## *Graduate Student Research Advising*

```{=tex}
\begin{cvpress}
 \cvpres
    {Amanda Laboy}
    {M.S., TAMU RWFM}
    {2023 -- Present}
 \cvpres
    {Kayla Art}
    {M.N.R.D., TAMU RWFM}
    {2023 -- Present} 
 \cvpres
    {Lulu Hoffman}
    {M.S., TAMU RWFM}
    {2023 -- Present}
 \cvpres
    {David Pearce}
    {M.S., TAMU RWFM}
    {2023 -- Present}
 \cvpres
    {Conner Ties}
    {M.S., TAMU RWFM}
    {2022 -- Present}
\end{cvpress}
```

## *Undergraduate Student Research Advising*

```{=tex}
\begin{cvpress}
 \cvpres
    {Daniel Whitman}
    {B.S., Macalester College REU}
    {2023 -- Present}
 \cvpres
    {Drake Dancila}
    {B.S., TAMU RWFM}
    {2022 -- 2023}
 \cvpres
    {Lulu Hoffman}
    {B.S., TAMU RWFM}
    {2022 -- 2023}    
\end{cvpress}
```

## *Secondary School Student Research Advising*

```{=tex}
\begin{cvpress}
 \cvpres
    {Sebastian Kuo}
    {H.S., Carnegie Vanguard High School}
    {2023 -- Present}
\end{cvpress}
```


## *Graduate Student Committee Member*

```{=tex}
\begin{cvpress}
 \cvpres
    {Jake Hanes}
    {M.S., TAMU SCSC}
    {2024 -- Present}
 \cvpres
    {Daniel Ramirez}
    {M.S., TAMU-Kingsville RWM}
    {2023 -- Present}
\end{cvpress}
```


## *Student Honors & Awards*

```{=tex}
\begin{cvpress}
  \cvpres
    {American Society of Mammalogists Student Travel Award}
    {David Pearce}
    {2024}
  \cvpres
    {AgGIE Leadership Community Student Development Grant}
    {Amanda Laboy}
    {2024}
  \cvpres
    {RWFM Graduate Student Travel Grant}
    {David Pearce}
    {2024}
 \cvpres
    {RWFM Graduate Student Travel Grant}
    {Conner Ties}
    {2024}
 \cvpres
    {COALS Merit Fellowship}
    {Amanda Laboy}
    {2023}
 \cvpres
    {RWFM Graduate Student Travel Grant}
    {Conner Ties}
    {2023}
  \cvpres
    {RWFM Graduate Student Travel Grant}
    {David Pearce}
    {2023}
 \cvpres
    {RWFM Excellence Award for Undergraduates}
    {Drake Dancila}
    {2023}
  \cvpres
    {RWFM Excellence Award for Undergraduates}
    {Lulu Hoffman}
    {2023}
\end{cvpress}

```

# Investigator Grants & Contracts

## *Funded (Total: $3,884,225, Lab Allocated: $385,595)*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {\textbf{TAMU AgriLife Research Rangeland Ecology and Management Research Funding}. 2024-2026. Developing proxies for rangeland assessments using drones. \textbf{\$106,700; \textit{Funded}}. PI: Humberto Perotto, Co-PIs: Sorin Popescu, \textbf{Ty J. Werdel (Lab Allocated: \$17,783)}, Jacob Lucero, Jeff Goodwin, and Morgan Treadwell.}
      \item {\textbf{TAMU AgriLife Research Rangeland Ecology and Management Research Funding}. 2024-2026. Working towards healthy rangelands: understanding the factors limiting the adoption of grazing, fire, and wildfire management practices among exurban landowners. \textbf{\$106,448; \textit{Funded}}. PI: David  Matarrita, Co-PIs: Rafael Landeverde, \textbf{Ty J. Werdel (Lab Allocated: \$26,612)}, and Morgan Treadwell.}
      \item {\textbf{TAMU AgriLife Research Animal Health and Disease Research Capacity Funding}. 2024-2025. The impact of osmotic stress on the catfish pathogen \textit{Aeromonas hydrophila}: Implications for managing motile \textit{Aeromonas} septicemia (MAS) in U.S. catfish farming. \textbf{\$100,000; \textit{Funded}}. PI: Haitham Mohammed, Co-PI: \textbf{Ty J. Werdel}.}
      \item {\textbf{Private Donation}. 2023. Student-led population ecology of fox squirrels on the TAMU campus. \textbf{\$10,000; \textit{Funded}}. PI: \textbf{Ty J. Werdel}.}
      \item {\textbf{USFWS}. 2023-2027. Evaluation and mitigation for sensitive state threatened and endangered wildlife. \textbf{\$3,399,877; \textit{Funded}}. Co-PIs: Marcus Blum, Paul Crump, Jacob Dykes, Whitney Gann, Andrew Gregory, Toby Hibbitts, Mathew Kramm, Roel Lopez, Kevin Moczygemba, Michael Morrison, Humberto Perotto, Wady Ryberg, Danielle Walkup, Stephen Webb, and \textbf{Ty J. Werdel (Lab Allocated: \$170,000)}.}
      \item {\textbf{Department of Rangeland, Wildlife and Fisheries Management}. 2023-2024. Long-term wildlife monitoring for unmanaged rangelands transitioning to planned grazing management. \textbf{\$100,000; \textit{Funded}}. PIs: Stephen L. Webb and \textbf{Ty J. Werdel}.}
      \item {\textbf{Private Donation}. 2023. Long-term wildlife monitoring for unmanaged rangelands transitioning to planned grazing management. \textbf{\$1,200; \textit{Funded}}. PI: \textbf{Ty J. Werdel}.}
      \item {\textbf{Department of Rangeland, Wildlife and Fisheries Management}. 2023-2025. River otter (\textit{Lontra canadensis}) population dynamics in Texas. \textbf{\$60,000; \textit{Funded}}. PI: \textbf{Ty J. Werdel}.}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

## *Unfunded Proposals*

\vspace{1\baselineskip}

```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
      \item {\textbf{TAMU AgriLife Research Rangeland Ecology and Management Research Funding}. 2024-2026. Resource selection and spatial interactions of native, exotic, and domestic ungulates on Texas rangelands. \textbf{\$150,000; \textit{Not Funded}}. PI: \textbf{Ty J. Werdel}, Co-PIs: Jacob E. Lucero, Humberto Perotto, and Jacob L. Dykes.}
      \item {\textbf{National Science Foundation}. 2023-2025. Incorporating Native American partnerships and knowledge into Great Plains fire science. \textbf{\$199,404; \textit{Not Funded}}. PI: David  Matarrita, Co-PIs: Bradford Wilcox  and \textbf{Ty J. Werdel}.}
      \item {\textbf{USDA APHIS Wildlife Services}. 2023-2024. Spatial interactions and potential disease transmission of free-ranging native and exotic ungulates. \textbf{\$225,437; \textit{Not Funded}}. PI: \textbf{Ty J. Werdel}.}
      \end{cvetar}
    }
\end{cvpubs}
```

\vspace{1\baselineskip}

# Honors & Awards

## *Awards ($121,150)*

```{=tex}
\begin{cvpress}
 \cvpres
    {Community Building Through Mentorship Conference Panel Travel Grant}
    {The Wildlife Society}
    {2022}
 \cvpres
    {Agriculture Dean and Director’s Award for Graduate Student Research}
    {Kansas State University}
    {2022}
 \cvpres
    {Advancing Agricultural Science Opportunities for Native Americans Scholarship}
    {AISES}
    {2021}
 \cvpres
    {Robert Nunemacher Scholarship}
    {Kansas State University}
    {2021}
 \cvpres
    {Advancing Agricultural Science Opportunities for Native Americans Research Award}
    {AISES}
    {2020}
 \cvpres
    {Advancing Agricultural Science Opportunities for Native Americans Scholarship}
    {AISES}
    {2020}
 \cvpres
    {Lighting the Pathway to Faculty Careers for Natives in STEM}
    {AISES}
    {2020}
 \cvpres
    {College of Agriculture Graduate Student Recognition of Achievement}
    {Kansas State University}
    {2020}
 \cvpres
    {AISES Together Towards Tomorrow T3 Scholarship}
    {AISES}
    {2020}
 \cvpres
    {Gamma Sigma Delta}
    {Kansas State University}
    {2019}
 \cvpres
    {AISES Travel Grant}
    {AISES}
    {2019}
 \cvpres
    {Advancing Agricultural Science Opportunities for Native Americans Scholarship}
    {AISES}
    {2019}
 \cvpres
    {Kansas State University Graduate Student Recognition of Achievement}
    {Kansas State University}
    {2019}
 \cvpres
    {College of Agriculture Graduate Student Recognition of Achievement}
    {Kansas State University}
    {2019}
 \cvpres
    {Inclusive Pedagogy Travel Grant}
    {The Wildlife Society}
    {2018}
 \cvpres
    {Life Membership Fund Scholarship}
    {Wild Sheep Foundation}
    {2018}
 \cvpres
    {Predoctoral Ford Fellowship}
    {(Honorable Mention) Ford Foundation Fellowships Program}
    {2018}
 \cvpres
    {Native Student Professional Development Grant}
    {The Wildlife Society}
    {2017}
 \cvpres
    {Launch Collegiate Business Pitch Competition}
    {Kansas State University}
    {2017}
 \cvpres
    {Native Student Professional Development Grant}
    {The Wildlife Society}
    {2016}
 \cvpres
    {Phi Kappa Phi Honor Society}
    {South Dakota State University}
    {2016}
 \cvpres
    {Excellence in Wildlife Management}
    {Chadron State College}
    {2013}
 \cvpres
    {Platinum Eagle Award}
    {(Finalist) Chadron State College}
    {2013}
 \cvpres
    {Gates Millennium Scholarship}
    {Bill and Melinda Gates Foundation}
    {2005}
 \cvpres
    {Scholastic Excellence in Engineering}
    {University of Wyoming}
    {2005}
 \cvpres
    {Scholars Stipend}
    {University of Wyoming}
    {2005}
 \cvpres
    {Computer Science, Engineering, and Mathematics Scholarship}
    {University of Wyoming}
    {2005}
 \cvpres
    {Honors Program}
    {University of Wyoming}
    {2005}
\end{cvpress}

```


# Professional Service

## *Executive Service in Professional Organizations*


```{r SERVICE}
service %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} -- {endMonth} {endYear}",.na = ""),
    where = where
  )
```

\vspace{1\baselineskip}

## *Working Group Membership*

```{=tex}
\begin{cvpress}
 \cvpres
    {Rangeland Wildlife Working Group}
    {The Wildlife Society}
    {2018 -- Present}
 \cvpres
    {Native Peoples' Wildlife Management Working Group}
    {The Wildlife Society}
    {2015 -- Present}
 \cvpres
    {Student Development Working Group}
    {The Wildlife Society}
    {2013 -- 2022}
\end{cvpress}
```

\vspace{1\baselineskip}

## *Chapter Membership*

```{=tex}
\begin{cvpress}
 \cvpres
    {Southwest Section}
    {The Wildlife Society}
    {2023 -- Present}
 \cvpres
    {Texas Chapter}
    {The Wildlife Society}
    {2023 -- Present}
 \cvpres
    {Central Mountains and Plains Section}
    {The Wildlife Society}
    {2018 -- 2022}
 \cvpres
    {Kansas Chapter}
    {The Wildlife Society}
    {2017 -- 2022}
 \cvpres
    {South Dakota Chapter}
    {The Wildlife Society}
    {2014 -- 2017}
 \cvpres
    {Nebraska Chapter}
    {The Wildlife Society}
    {2013 -- 2014}
 \cvpres
    {Chadron State Student Chapter}
    {The Wildlife Society}
    {2012 -- 2013}
\end{cvpress}
```

\vspace{1\baselineskip}

## *Professional Organization Membership*

```{=tex}
\begin{cvmemb}
 \cvmem
    {Society for Range Management}
    {}
    {2023 -- Present}
 \cvmem
    {Society for Advancement of Chicanos/Hispanics and Native Americans in Science}
    {}
    {2021 -- Present}
 \cvmem
    {Gamma Sigma Delta Honor Society}
    {}
    {2019 -- Present}
 \cvmem
    {American Indian Science and Engineering Society}
    {}
    {2019 -- Present}
 \cvmem
    {Swift Fox Conservation Team}
    {}
    {2018 -- Present}
 \cvmem
    {Phi Kappa Phi Honor Society}
    {}
    {2016 -- Present}
 \cvmem
    {Native American Fish and Wildlife Society}
    {}
    {2015 -- Present}
 \cvmem
    {Rocky Mountain Bighorn Society}
    {}
    {2015 -- 2017}
 \cvmem
    {Wild Sheep Foundation}
    {}
    {2014 -- 2020}
 \cvmem
    {American Society of Mammalogists}
    {}
    {2013 -- Present}
 \cvmem
    {The Wildlife Society}
    {}
    {2013 -- Present}
\end{cvmemb}
```

\vspace{1\baselineskip}

## *External Journal Reviewer (10)*
```{=tex}
\begin{cvmemb}
 \cvmem
    {Movement Ecology}
    {}
    {2024}
 \cvmem
    {The Journal of Wildlife Management}
    {(2)}
    {2023, 2023}
 \cvmem
    {Journal of Fish and Wildlife Management}
    {}
    {2023}
 \cvmem
    {PeerJ}
    {(2)}
    {2022, 2023}
 \cvmem
    {Frontiers in Ecology and the Environment}
    {}
    {2023}
 \cvmem
    {Science}
    {}
    {2023}
 \cvmem
    {Canadian Journal of Zoology}
    {}
    {2022}
 \cvmem
    {Journal of Mammalogy}
    {}
    {2021}
\end{cvmemb}
```


\vspace{1\baselineskip}

# University Service

## *Texas A&M University*

```{=tex}
\begin{cvpress}
 \cvpres
    {Faculty Reviewer}
    {Avilés-Johnson Fellowship Program}
    {2024} 
 \cvpres
    {Faculty Advisor}
    {TAMU Student Chapter of The Wildlife Society}
    {2023 -- Present}
\end{cvpress}
```

\vspace{1\baselineskip}

## *Department*

```{=tex}
\begin{cvpress}
 \cvpres
    {OEM Curriculum Committee}
    {RWFM}
    {2023 -- Present}
 \cvpres
    {Awards Committee}
    {RWFM}
    {2023 -- Present}
 \cvpres
    {Undergraduate Committee}
    {RWFM}
    {2023 -- Present}  
 \cvpres
    {Caesar Kleberg Chair Search Committee}
    {RWFM}
    {2023 -- 2024}
\end{cvpress}
```

\vspace{1\baselineskip}

# Presentations

## *Contributed* (*Werdel Wildlfe Lab Member)
\vspace{1\baselineskip}
```{=tex}
\begin{cvpubs}
    {
      \begin{cvetar}
       \item {Laboy, A.\textbf{*}, R. Lopez, and \textbf{T.J. Werdel}. \textbf{2024}. Evaluating small mammal biodiversity using camera traps. \textbf{\textit{Ecological Integration Symposium, College Station, TX}}.}
       \item {Laboy, A.\textbf{*}, R. Lopez, and \textbf{T.J. Werdel}. \textbf{2024}. Evaluating small mammal biodiversity using camera traps. \textbf{\textit{Diversity in Science Symposium, College Station, TX}}.}
       \item {Laboy, A.\textbf{*}, R. Lopez, and \textbf{T.J. Werdel}. \textbf{2024}. Evaluating small mammal biodiversity using camera traps. \textbf{\textit{TAMU Student Research Week, College Station, TX}}.}
       \item {\textbf{Werdel, T.J.}, D. Matarrita-Cascante, and J.E. Lucero. \textbf{2024}. State of traditional ecological knowledge in the wildlife management profession. \textbf{\textit{Texas Chapter of The Wildlife Society Annual Conference, Houston, TX}}.}
       \item {Ties, C.\textbf{*}, S.L. Webb, and \textbf{T.J. Werdel}. \textbf{2024}. Mapping collared peccary habitat: species distribution modeling in the South Texas Plains and Trans-Pecos ecoregions. \textbf{\textit{Texas Chapter of The Wildlife Society Annual Conference, Houston, TX}}.}
      \item {Palomo-Muñoz, G., \textbf{T.J. Werdel}, C.W. Piper, M. Fidino, T. Gallo, M.S. Peek, A.M. Ricketts, and A.A. Ahlers. \textbf{2024}. Habitat use by black-tailed jackrabbits and eastern cottontail rabbits in a multipredator landscape. \textbf{\textit{Kansas Natural Resources Conference, Manhattan, KS}}.}
      \item {Ties, C.\textbf{*}, S.L. Webb, and \textbf{T.J. Werdel}. \textbf{2023}. Using community science to determine collared peccary spatial distribution in Texas. \textbf{\textit{The Wildlife Society 30th Annual Conference, Louisville, KY}}.}
      \item {Ties, C.\textbf{*}, S.L. Webb, and \textbf{T.J. Werdel}. \textbf{2023}. Mapping collared peccary habitat: species distribution modeling in the south Texas plains. \textbf{\textit{Texas Section Society For Range Management, Bastrop, TX}}.}
      \item {Whitman, D.\textbf{*} and \textbf{T.J. Werdel}. \textbf{2023}. Campus fox squirrel presence influenced by fine-scale landscape characteristics. \textbf{\textit{Macalester College Summer Showcase, Saint Paul, MN}}.}
      \item {Dancila, A.D.\textbf{*}, \textbf{T.J. Werdel}, S.M. Chinn, J.C. Beasley, and S.L. Webb. \textbf{2023}. Analysis of reproductive parameters of wild pigs in southcentral Oklahoma. \textbf{\textit{RWFM Convocation, College Station, TX}}.}
      \item {Hoffman, M.G.\textbf{*}, M.D. Proctor, \textbf{T.J. Werdel}, and S.L. Webb. \textbf{2023}. Activity patterns and potential interactions among cattle, white-tailed deer, and wild pigs. \textbf{\textit{RWFM Convocation, College Station, TX}}.}
      \item {Whitman, D.\textbf{*} and \textbf{T.J. Werdel.}. \textbf{2023}. Fine-scale landscape features influence fox squirrel presence on urban campus. \textbf{\textit{LAUNCH Summer Undergraduate Research Symposium, College Station, TX}}.}
      \item {Whitman, D.\textbf{*} and \textbf{T.J. Werdel}. \textbf{2023}. Campus fox squirrel presence influenced by fine-scale landscape characteristics. \textbf{\textit{College of Agriculture and Life Sciences Summer Undergraduate Research Symposium, College Station, TX}}.}
      \item {Hoffman, M.G.\textbf{*}, \textbf{T.J. Werdel}, M.D. Proctor, and S.L. Webb. \textbf{2023}. Activity patterns and potential interactions among cattle, white-tailed deer, and wild pigs. \textbf{\textit{Ecological Integration Symposium, College Station, TX}}.}
      \item {Dancila, A.D.\textbf{*}, \textbf{T.J. Werdel}, S.M. Chinn, J.C. Beasley, and S.L. Webb. \textbf{2023}. Analysis of reproductive parameters of wild pigs in southcentral Oklahoma. \textbf{\textit{TAMU Student Research Week, College Station, TX}}.}
      \item {Hoffman, M.G.\textbf{*}, M.D. Proctor, \textbf{T.J. Werdel}, and S.L. Webb. \textbf{2023}. Activity patterns and potential interactions among cattle, white-tailed deer, and wild pigs. \textbf{\textit{TAMU Student Research Week, College Station, TX}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M.S. Peek, D.S. Sullins, and A.A. Ahlers. \textbf{2023}. Strategic grassland conservation for swift foxes in multi-use landscapes. \textbf{\textit{Texas Chapter of The Wildlife Society Annual Conference, Houston, TX}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, M.S. Peek, A.M. Ricketts, and A.A. Ahlers. \textbf{2023}. Landscape-scale effects structure carnivore communities in an agro-prairie ecosystem. \textbf{\textit{Kansas Natural Resources Conference, Manhattan, KS}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, M.S. Peek, A.M. Ricketts, D.S. Sullins, and A.A. Ahlers. \textbf{2023}. Strategic grassland conservation for swift foxes in multi-use landscapes. \textbf{\textit{Kansas Natural Resources Conference, Manhattan, KS}}.}
      \item {Palomo-Muñoz, G., \textbf{T.J. Werdel}, C.W. Piper, M. Fidno, A.M. Ricketts, and A.A. Ahlers. \textbf{2022}. Local-scale habitat structure mediates interactions between coyotes and lagamorphs. \textbf{\textit{101st Annual Meeting of the American Society of Mammalogists, Tucson, AZ}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2021}. Scale-specific landscape effects impose range-limiting constraints on the distribution of swift foxes. \textbf{\textit{The Wildlife Society 28th Annual Conference, Virtual}}.}
      \item {Piper, C.W, \textbf{T.J. Werdel}, A.M. Ricketts, D. Sullins, M. Peek, and A.A. Ahlers. \textbf{2021}. Landscape composition and proximity to water structure American badger distributions in shortgrass prairies. \textbf{\textit{The Wildlife Society 28th Annual Conference, Virtual}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2021}. Multiscale landscape effects impose range-limiting constraints on the distribution of swift fox. \textbf{\textit{Swift Fox Conservation Team Meeting, Virtual}}.}
      \item {\textbf{Werdel, T.J.}, C.W. Piper, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2021}. Multiscale landscape effects impose range-limiting constraints on the distribution of swift fox. \textbf{\textit{Midwest Association of Fish and Wildlife Agencies Furbearer Workshop, Virtual}}.}
      \item {Piper, C.W, \textbf{T.J. Werdel}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2021}. Landscape composition and proximity to water structure American badger (\textit{Taxidea taxus}) distributions in shortgrass prairies. \textbf{\textit{Midwest Association of Fish and Wildlife Agencies Furbearer Workshop, Virtual}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2020}. Assessing factors that influence occupancy and colonization of swift fox in western Kansas. \textbf{\textit{Kansas Natural Resources Conference, Manhattan, KS}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2019}. Assessing factors that shape carnivore diversity in shortgrass prairie ecosystems. \textbf{\textit{American Fisheries Society and The Wildlife Society 2019 Joint Annual Conference, Reno, NV}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2019}. Carnivore richness and diversity is driven by landscape change in shortgrass prairie ecosystems. \textbf{\textit{99th Annual Meeting of the American Society of Mammalogists, Washington, D.C}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2019}. Landscape effects on swift fox occupancy in western Kansas. \textbf{\textit{Southwest/Midwest Joint Furbearer Meeting, Enid, OK}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, and A.A. Ahlers. \textbf{2019}. Landscape change structures carnivore communities in shortgrass prairie ecosystems. \textbf{\textit{Kansas Natural Resources Conference, Manhattan, KS}}.}
      \item {\textbf{Werdel, T.J.}, A.M. Ricketts, M. Peek, and A.A. Ahlers. \textbf{2018}. Assessing the spatial distribution of swift fox in western Kansas. \textbf{\textit{The Wildlife Society 25th Annual Conference, Cleveland, OH}}.}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks. \textbf{2018}. Survival of bighorn sheep in the Deadwood region of the Black Hills. \textbf{\textit{Nebraska/Central Mountains and Plains Section of The Wildlife Society Annual Meeting, Kearney, NE}}.}
      \item {\textbf{Werdel, T.J.}, J.A. Jenks, J. Kanta, and C. Lehman. \textbf{2016}. Evaluation of the Deadwood bighorn sheep herd translocation. \textbf{\textit{The Wildlife Society 23rd Annual Conference, Raleigh, NC}}.}
      \item {\textbf{Werdel, T.J.}. \textbf{2013}. Small mammal population and diversity in relation to prairie dog reintroduction sites. \textbf{\textit{Sevilleta LTER Research Experience for Undergraduates Summer Symposium, Socorro, NM}}.}
      \end{cvetar}
    }
\end{cvpubs}
```



\vspace{1\baselineskip}
## *Invited*

```{r INVITED}
invited %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```


\vspace{1\baselineskip}
## *Guest Lectures*

```{r GUEST}
guest %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )
```